Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-05 paper.tex
Spell check in overleaf

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genomewide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of purely neutral simulations are
appropriate for the question and genomic partition under study.
A major strength of \msprime, however, is that it can be used in conjunction
with forwards-time simulators, enabling the simulation of
more realistic models than otherwise
possible~\citep{kelleher2018efficient,haller2018tree}.

@@

% jk: I started writing a roadmap here, but it's quite hard to do concisely
% and you either end up leaving sections out, or just summarising them
% one-by-one which makes it long and tedious. I think readers can either read
% through fully if they're interested, or just skim the section titles which
% should give them a good idea of whether they want to read it or not.

>>>>

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genome wide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of purely neutral simulations are
appropriate for the question and genomic partition under study.
A major strength of \msprime, however, is that it can be used in conjunction
with forwards-time simulators, enabling the simulation of
more realistic models than otherwise
possible~\citep{kelleher2018efficient,haller2018tree}.

@@
